### 2024-07-17 Scripts/Manuscript/manuscript.Rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Project Administration"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Bakker, M."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Wicherts, J.M."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Project Administration"
      - "Supervision"
      - "Validation"
      - "Writing - Review & Editing"

@@

abstract: |
  The credibility of psychological science and the ability to replicate earlier findings require good measurement.
   Here, we assessed the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original psychological studies. 
   We investigated their associations with replicability.
   The results indicated that not all measures in the original and replication studies were sufficiently reliable across contexts. 
   Additionally, evidence on reliability and validity was rarely reported. 
   Finally, incompleteness in measurement reporting in replication studies was associated with lower replicability of the findings tested with that measure. 
   These findings indicate a worrying lack of reported validating evidence for measurement in the literature, and its harm to credibility.
   We offer suggestions on improving measurement validation and reporting practices, and argue that researchers should evaluate the reported measurement information when deciding what studies to replicate.

keywords          : "reliability, validity, measurement, reporting, replicability, credibility"
wordcount         : "135"

@@

For solid scientific progress in psychology, we need to be able to rely on previous findings - findings should be credible. Unfortunately, psychology seems to face several threats to the credibility of its findings. In this article, we investigate how the credibility of psychological findings may be affected by problems in psychological measurement, and in turn, how those problems may affect subsequent replications.

@@

A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving]. This means that the observed effect should be comparable across the original study and subsequent replications if the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].

But replications often fail. In 2015, the Replication Project: Psychology (RPP) attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings [@osc2015estimating]. Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many], and often found smaller effects in replications compared to original research. Furthermore, the estimates of the effect varied between different lab locations.

In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain failures to replicate. The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. Another factor that has gained more traction recently is the impact of measurement-related challenges on replicability and credibility.

@@

Psychological constructs, such as affective state or intelligence, can not be measured directly [@flake2017construct]. Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.

@@

## Many Labs Sample Description

Because the Many Labs projects involved multiple lab locations over the world directly replicating the same effect, their data allows us to study the variability in these measures across different contexts. Furthermore, the Many Labs projects used preregistered and documented structured protocols, we therefore believe the measurement use in these projects represent a high standard within the field. Any issues in measurement here is thus taken as an indication that other replications are equally if not more likely to face the same issues.

@@

While reliability is generally considered a measure specific feature, this is false. The reliability of a measure varies between samples, and thus  [@cho2015cronbach; @pauly2018resampling]. Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring]. For instance, measures are known to generally show lower reliability in more homogeneous samples as compared to heterogeneous samples [@pike1998reliability].

@@

Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon. QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a conjugate term to Questionable Research Practices [QRPs, @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. More specifically,  @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. If these questions can be answered based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.

@@

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers. In order to reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores. If the measure is not reconstructed exactly, constructs measured by original and replication may differ. leading to differences in effect size estimates irrespective of the credibility of the original effect.

@@

Our study investigated the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects. First, this study expands on the research by @stanley2014expectations. Our goal was to see whether reliability was related to replication success on empirical replication data. Specifically, we investigated whether replicated studies differed in their reliability from non-replicated studies.  @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification. Therefore, to add further context to the relation between reliability and replication, this study also investigated the variation in reliability as observed across labs.

@@

The Many Labs studies were intended as direct replications. In direct replications, any deviations from the original research are believed to be irrelevant for testing the same effect as the original study [@nosek2022replicability]. In that case, the reliability of measurements in replications should also not deviate systematically from the original research.

@@

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/9r8yt/>. Deviations from the preregistration are explicitly mentioned in the text.

### Data, materials, and online resources

@@

### Unit of analysis

The unit of analysis in this study was a measure of a psychological construct used in the primary analysis that was being replicated.  We used the the replication protocols to identify these measures. Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.

@@

To be included in the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses entirely. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles. Cronbach's Alpha was calculated using the alpha function from the psych R package [@R-psych] with default arguments. Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing]. The results based on Omega can be found in [Appendix C](AppendixScripts/Appendix_multilevel_analyses.Rmd).

@@

After the initial coding, we made a small revision to the preregistered coding protocol, because `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items were considered too stringent in some of their criteria for what constituted a QMP. For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with our initial protocol can be found in [Appendix D](AppendixScripts/Appendix_initial_QMP_analyses.Rmd).

@@

Every hypothesis test in this study was a two-sided test with an alpha of .05. No correction for multiple testing was applied, to ensure that the rate of false negatives remained low. Our hypotheses are about associations that to the authors' knowledge have been proposed in the literature, but not yet empirically tested on real data. In this exploratory context, false negatives were considered more harmful than false positives.

@@

The number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications can be seen in Table \@ref(tab:ReplicationRatioTable), for each of the Many Labs separately and in total.

@@

Our data had a multilevel structure. Each replication was nested within one of four Many Labs projects. Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^1]. Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication. The total sample size in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies.

@@

The RG meta-analysis was performed using the *rma* function from the *metafor* R package [@R-metafor]. Defaults settings were used. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

@@

### H1

@@

The number of reported reliabilities were `r N_reported_reliabilities_original` in original articles and `r N_reported_reliabilities_replications` in replications, which was too low to ensure that the pre-registered Mann-Whitney U test can function as an informative test on the difference in the reported value of Cronbach's Alpha between original articles and replications. Instead, the difference between the reported reliability in the original article and the calculated average reliability in replications is displayed in the Diff column in Figure \@ref(fig:Plot23AlphaCode). Contrary to Hypothesis 1, this column shows that the reported reliability in original articles was generally lower than the average reliability in the replication sample. Still, more than half of the reported reliabilities did fall within the 95-percentile range around the replication average.

### H2

To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities in the replications. This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Appendix A](AppendixScripts/Appendix_pre-reg_analyses.Rmd)).

@@

### H3

@@

# well this OR is quite a ridiculous number now..., but then again a step from 0 alpha to 1, is quite a jump too...
H3_test_result_main_alpha$full_result$alpha

@@

Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`). Results based on the Omega coefficient lead to a similar conclusion (see [Appendix C](AppendixScripts/Appendix_omega_analyses.Rmd). However, it should be noted that the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures. As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.

@@

Reliability was more commonly reported in original (n = `r `N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`. Validity evidence was similarly reported infrequently. `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles reported validity evidence from a factor analysis, while only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications did.

### H4

@@

We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [@R-betareg_a; @R-betareg_b]. Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of $(0, 1)$, including ratios. Furthermore, they are robust for heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].

@@

### H5

@@

H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)
H5_test_results_REV_with_OR

@@

We used logistic regression to test the association between the QMP ratio in replication protocols and replication success. In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`).

### H6

@@

@@

Using a beta regression model, we found total QMP ratio in the original article to be significantly related to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`). This result provides evidence in favor of Hypothesis 6.

@@

In this article, we analyzed the data, protocols, and related original articles from four Many Labs replication projects to assess reliability and measurement (reporting) practices. We additionally looked at how these features might be related to replication success, as a proxy of the credibility of findings. Overall, even though the average reliability was relatively high, we found that not all measures were sufficiently reliable, nor where measures always equally reliable in each setting in which they were used. Although, we did not observe reliability to significantly predict replication success, we did observe a negative relation between replication success and presence of QMPs in replication research. Finally, we found QMPs in the replication to be positively associated with QMPs in the original studies

@@

### Reliability varied within and between measures

@@

### No observed relation between reliability and replicability
@stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments. However, we observed no relation between reliability and replicability, even though our chosen replication index did not attenuate for measurement error. This result is surprising not only because it runs counter to the findings of @stanley2014expectations and Hypothesis 3. It also runs counter to the fact that according to statistical theory, the increased noise in the data as the result of lower reliability decreases the effect size estimates based on those data.

However, the relationship between reliability and replicability is complex [@willson1980research; @lebreton2014corrections; @oswald2015Imperfect; @zhang2024Metaanalysis]. For example, reliability and replicability are only related when the true effect is not null. In our sample more than half of the effects were not replicated, indicating that many of these effects may be null effects. For these effects no relation is expected. Furthermore, while lower reliability decreases effect sizes it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow]. As a result, effect estimates from various studies will appear more similar than they truly are, seemingly replicating the original. These and other relations are further complicated by the fact that reliability is not a fixed aspect of a scale, but a feature of that scale within a sample [e.g., @vacha1999practices; @cho2015cronbach].

The complexity of the relationship combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides a likely explanation for our non-significant finding.

The small number of relevant measures and reported reliabilities also indicates an important issue: we observed a lack of reliability evidence in both original and replication psychological research.

@@

### Measurement Reporting is often incomplete

@@

### Incomplete measurement reporting hinders replicability

@@

However, it is worth noting that these associations were only found for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Appendix D](AppendixScripts/Appendix_initial_QMP_analyses.Rmd) for results based on the initial protocol).

@@

# (APPENDIX) Appendix {.unnumbered}

```{r child = "AppendixScripts/Appendix_pre-reg_analyses.Rmd"}
```

```{r child = "AppendixScripts/Appendix_multilevel_analyses.Rmd"}
```

```{r child = "AppendixScripts/Appendix_omega_analyses.Rmd"}
```

```{r child = "AppendixScripts/Appendix_initial_QMP_analyses.Rmd"}
```

>>>>

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"

  - name          : "Bakker, M."
    affiliation   : "1"

  - name          : "Wicherts, J.M."
    affiliation   : "1"

  - name          : "Nuijten, M.B."
    affiliation   : "1"

@@

  The authors made the following contributions. CG: Conceptualization, Data curation, Formal Analysis, Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft Preparation, Writing - Review & Editing; MB: Conceptualization, Supervision, Writing - Review & Editing; JW: Conceptualization, Supervision, Writing - Review & Editing; MN: Conceptualization, Project Administration, Supervision, Validation, Writing - Review & Editing.

abstract: |
  Recent studies have shown that challenges in measurement practices in original and replication research may have contributed to the “replication crisis” in psychological science. 
  However, the exact nature and extent of the association between measurement and replicability is not yet clear. 
  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] and related original psychological studies, and whether these were associated with replicability.
  Results from logistic regression models indicated that questionable practices in measurement reporting in replication studies (b = -5.60, OR = 0.004, 95% [0,0.156]), but not the reliability of the measurement (b = 8.21, OR = 3677.542, 95% [1.271,1727601729.241]), was associated with lower replicability of the findings tested with that measure. <!-- the code for these two results is: ???; these lines will only work after code chunks 1, 2, 12, & 19 have been ran. -->
  Furthermore, not all measures in the original and replication studies were sufficiently reliable across contexts. 
  Additionally, we found that evidence on reliability and validity was rarely reported. 
  These findings corroborate existing research that shows that validity evidence is rarely reported, and that these reporting practices may have negative consequences for the informativeness of replications. 
  We offer suggestions on improving measurement validation and reporting practices. 
  Finally, we argue that researchers should evaluate the reported measurement information when deciding what studies to replicate.

keywords          : "reliability, validity, measurement, reporting, replicability, credibility, psychology"
wordcount         : "203"

@@

For solid scientific progress in psychology, we need to be able to rely on previous findings - findings should be credible. Unfortunately, psychology seems to face several threats to the credibility of its findings. In this article, we investigate how the credibility of psychological findings may be related to problems in psychological measurement, and in turn, how those problems may affect subsequent replications.

@@

A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving]. This means that the observed effect should be comparable across the original study and subsequent replications in new samples if the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].

But replications often fail. In 2015, the Replication Project: Psychology [RPP; @osc2015estimating] attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings . Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many], and often found smaller effects in replications compared to original research. Furthermore, the estimates of the effect varied between different lab locations.

In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain the low replication rate. The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. Another factor that has gained more traction recently is the impact of measurement-related challenges on replicability and credibility.

@@

Psychological constructs, such as affective state or intelligence, cannot be measured directly [@flake2017construct]. Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.

@@

Because the Many Labs projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] are large-scale collaborations in which multiple lab locations directly replicated the same set of studies, their data allows us to study the variability in their measures across different contexts. Furthermore, as the Many Labs projects used preregistered and documented structured protocols, we therefore believe the measurement use in these projects represent a high standard within the field. Any issues in measurement here might suggest that other replications could face similar or greater challenges.

@@

While reliability is generally considered a measure specific feature, this is false. The reliability of a measure varies between samples [@cho2015cronbach; @pauly2018resampling]. Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring]. For instance, measures are known to generally show lower reliability in more homogeneous samples as compared to heterogeneous samples [@pike1998reliability].

@@

Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon. QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a term analogous to Questionable Research Practices [QRPs, @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement]. More specifically,  @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. If these questions can be answered based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.

@@

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers. In order to reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores. If the measure is not reconstructed exactly, constructs measured by original and replication may differ, which may lead to differences in effect size estimates irrespective of the credibility of the original effect.

@@

Our study investigated the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects. First, this study expands on the research by @stanley2014expectations. Our goal was to see whether reliability was related to replication success in empirical replication data. Specifically, we investigated whether successfully replicated studies differed in reliability from non-replicated studies. @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification. Therefore, to add further context to the relation between reliability and replication, this study also investigated the variation in reliability as observed across labs.

@@

The Many Labs studies were intended as direct replications. In direct replications, any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability]. This means that, the reliability of measurements in replications should also not deviate systematically from the original research.

@@

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. Deviations from the preregistration are explicitly mentioned in the text.

### Data, Materials, and Online Resources

@@

### Unit of Analysis

The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was being replicated. Multiple psychological constructs could be measured per original study or replication. We used the the replication protocols to identify these measures. Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.

@@

To be included in the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles. Cronbach's Alpha was calculated using the alpha function from the psych R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych] with default arguments. Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing]. The results based on Omega can be found in [Appendix C](../../SupplementaryMaterials/AppendixScripts/Appendix_multilevel_analyses.Rmd).

@@

After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because they were considered too stringent in some of their criteria for what constituted a QMP. For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Appendix D](../../SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.Rmd).

@@

Every hypothesis test in this study was a two-sided test with an alpha of .05. No correction for multiple testing was applied, to ensure that the rate of false negatives remained low. Our hypotheses are about associations that have been proposed in the literature, but to the best of our knowledge have not yet been empirically tested on real data. In this exploratory context, false negatives were considered more detrimental than false positives.

@@

Table \@ref(tab:ReplicationRatioTable) shows the number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications, for each of the Many Labs separately and in total.

@@

Our data had a multilevel structure. Each replication was nested within one of four Many Labs projects. Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^1]. Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

@@

The RG meta-analysis was performed using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor]. Defaults settings were used. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

@@

### Hypothesis 1: Reliability Reporting in Original Compared to Replication Research.

@@

The number of reported reliabilities was `r N_reported_reliabilities_original` in original articles and `r N_reported_reliabilities_replications` in replications, which was too low to ensure that the pre-registered Mann-Whitney U test can function as an informative test on the difference in the reported value of Cronbach's Alpha between original articles and replications. Instead, the difference between the reported reliability in the original article and the calculated average reliability in replications is displayed in the Diff column in Figure \@ref(fig:Plot23AlphaCode). Contrary to Hypothesis 1, this column shows that the reported reliability in original articles was generally lower than the average reliability in the replication sample. Still, more than half of the reported reliabilities did fall within the 95-percentile range around the replication average.

### Hypotheis 2: Within Study Variation in Reliability.

To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities in the replications. This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Appendix A](../../SupplementaryMaterials/AppendixScripts/Appendix_pre-reg_analyses.Rmd)).

@@

### Hypotyhesis 3: Reliability and Replicability

@@

# well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...
H3_test_result_main_alpha$full_result$alpha

@@

Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`). Results based on the Omega coefficient lead to a similar conclusion (see [Appendix C](../../SupplementaryMaterials/AppendixScripts/Appendix_omega_analyses.Rmd)). However, it should be noted that the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures. As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.

@@

Reliability was more commonly reported in original (n = `r N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`. Validity evidence was similarly reported infrequently. `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles reported validity evidence from a factor analysis, while only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications did.

### Hypothesis 4: QMPs in Original Compared to Replication Research.

@@

We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*; @R-betareg_a; @R-betareg_b]. Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of $(0, 1)$, including ratios. Furthermore, they are robust for heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].

@@

### Hypothesis 5: Replication Research QMPs and Replicability.

@@

H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)

# and the same model using the QMPs from the initial coding protocol
H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))

H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE, not_significant = TRUE)

@@

We used logistic regression to test the association between the QMP ratio in replication protocols and replication success. In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`). However, we did not find the association when based on the initial protocol (`r H5_test_results_with_OR`).

### Hypothesis 6: Relation Between QMPs in Original and Replication Research.

@@

# and the same model using the QMPs from the initial coding protocol
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

Using a beta regression model, we found total QMP ratio in the original article to be significantly related to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`). This result provides evidence in favor of Hypothesis 6. However, this association was sensitive to changes in the QMP protocol, as we did not observe a significant relation between original and replication QMP ratios based on QMPs from the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).

@@

In this article, we analyzed the data, protocols, and related original articles from four Many Labs replication projects to assess reliability and measurement (reporting) practices. We additionally looked at how these features might be related to replication success, as a proxy of the credibility of findings. Overall, even though the average reliability was relatively high, we found that not all measures were sufficiently reliable, nor where measures always equally reliable in each setting in which they were used. Although we did not observe reliability to significantly predict replication success, we did observe a negative relation between replication success and presence of QMPs in replication research. Finally, we found QMPs in the original studies to be positively associated with QMPs in the replications.

@@

### Reliability Varied Within and Between Measures

@@

### No Observed Relation Between Reliability and Replicability
@stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments. However, we observed no relation between reliability and replicability, even though our chosen replication index did not attenuate for measurement error. This result is surprising not only because it runs counter to the findings of @stanley2014expectations and Hypothesis 3. It also runs counter to the fact that according to statistical theory, the increased noise in the data as the result of lower reliability decreases the effect size estimates based on those data.

However, the relationship between reliability and replicability is complex [@willson1980research; @lebreton2014corrections; @oswald2015Imperfect; @zhang2024Metaanalysis]. For example, reliability and replicability are only related when the true effect is not null. In our sample, more than half of the effects were not replicated, indicating that many of these effects may be null effects. For these effects no relation between reliability and replicability is expected. Furthermore, while lower reliability decreases effect sizes it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow]. As a result, effect estimates from various studies will appear more similar than they truly are, seemingly replicating the original. These and other relations are further complicated by the fact that reliability is not a fixed aspect of a scale, but a feature of that scale within a sample [e.g., @vacha1999practices; @cho2015cronbach].

The complexity of the relationship combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides another possible explanation for our non-significant finding. The small number of relevant measures and reported reliabilities also indicates an important issue: we observed a lack of reliability evidence in both original and replication psychological research.

@@

### Measurement Reporting is Often Incomplete

@@

### Incomplete Measurement Reporting Hinders Replicability

@@

However, it is worth noting that these associations were only found for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Appendix D](../../SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.Rmd) for results based on the initial protocol).

@@
